Outstanding Title

### 2017-02-23 writing/EpiDraft.Rmd
Add to simulating data section

Simulation studies are important in environmental epidemiology research on air pollution, temperature, and other exposures. For example, simulated data can be used to test new statistical models and perform power analyses. Developing the code to simulate environmental time series for these types of studies can be time consuming, and simulation methods have varied across previous simulation studies [cite studies], complicating the comparison of results across different studies.

@@

#Previous Simulation Studies

@@

>>>>

Simulation studies are important in environmental epidemiology research on air pollution, temperature, and other exposures. For example, simulated data can be used to test new statistical models and perform power analyses. Two current challenges of simulating time series data for epidemiology studies are (1) methods for simulating are inconsistent, making it difficult to compare results from different studies, and (2) developing the code to simulate environmental time series for these types of studies can be time consuming. We introduce eesim, an open-source software package in R that offers a solution to these challenges.

Paragraph about previous simulation studies

@@

@@

[Chart / Figure of functions included and simulation process]

This package allows you to simulate time series of environmental health data and perform simulation-based power analyses and other measures of model performance. The package includes four main parts:

1. Generation of exposure data; 
2. Generation of outcome data;
3. Fitting models to simulated data; and 
4. Evaluating model performance on simulated data.

The user has the option to customize different aspects of the simulation at each of these steps.

The main function of this package is the `eesim` function. You can use the `eesim` function to conduct all four steps of the simulation process outlined above at once.

The `eesim` function requires several arguments, both numeric and character, including the desired number of repetitions of the simulation, the sample size for each repetiton, the type of exposure values (binary or continous), the expected average value of the response variable, the relative risk, and the type of model desired. The user has the option to input more arguments specifying trends or custom functions for the exposure, the outcome, or both.

The `eesim` function returns a list with two elements. The first element gives simulation-specific results: the estimated effect size, standard error, t- and p-values, and upper and lower 95% confidence bounds when a model was applied to each set of simulated data. The second element gives some measures of model assessment, assessed over all simulations, including the mean effect size and relative risk estimates across simulations.

[insert equation here?]

For example, you can use the following call to (1) generate 3 repetitions of 100 observations of a continuous exposure with mean 50 and standard deviation 5, with a seasonal trend in expected value; (2) generate 10 associated outcome values, where the outcome has an average value of 20 and a relative risk of 1.10 per one-unit increase in the exposure; (3) fit a generalized linear model that controls for long-term and seasonal trends with a natural cubic spline with 2 degrees of freedom per year; and (4) evaluate the performace of that model on the simulated data:

```{r}
library(eesim)
eesim(n_reps = 3, n = 100, central = 50, sd = 5, exposure_type = "continuous", 
      outcome_trend = "curvilinear", average_outcome = 20, rr = 1.10, model = "spline", df_year = 2)
```

The above output gives the estimated effect sizes for each of the three repetitions along with their standard errors, test statistics, p-values, and confidence intervals. It also summarizes the outcomes of all three repetitions with a mean estimated beta (which equals the log of the estimated relative risk), estimated relative risk, the variance of the estimated betas, and the mean variance of the individual betas.

### 2017-02-23 writing/JSSDraft/JSSDraft.Rmd
Add to simulating data section

For example, \citet{Bellan2015} used a simulation study to determine the power and statistical validity of two potential Ebola vaccine trials, a randomized controlled trial and a stepped-wedge cluster trial. Simulation was useful in this case because the trial would be conducting in a population with clustering by geographical district and with a temporally changing hazard of Ebola infection over the trial period \citep{Bellan2015}.

>>>>

For example, \citet{Bellan2015} used a simulation study to determine the power and statistical validity of two potential Ebola vaccine trials, a randomized controlled trial and a stepped-wedge cluster trial. Simulation was useful in this case because the trial would be conducted in a population with clustering by geographical district and with a temporally changing hazard of Ebola infection over the trial period \citep{Bellan2015}.
